HTW Model e1

### 2024-03-24 Model/htw_model.qmd
let's try that again

invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
invisible(list2env(load_e1(), envir = .GlobalEnv))
e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
```

@@

@@

```{r}
#| label: fig-htw-post-dist
#| fig-cap: Posterior Distributions of $c$ and $lr$ parameters. Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median. Note that the y axes of the plots for the c parameter are scaled logarithmically.
#| fig-height: 6
#| fig-width: 10

@@

lr_post <- post_dat_avg %>%
    group_by(id, condit, Model, Fit_Method, rank) %>%
    slice_head(n = 1) |>
    ggplot(aes(y=lr, x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.4)) +
    ggh4x::facet_nested_wrap(~Model) + labs(title="learning rate parameter") +
  theme(legend.title = element_blank(), legend.position = "none",plot.title=element_text(hjust=.5))
c_post + lr_post
```

@@

@@

# pdl <- post_dat_l |> rename("bandInt"=x) |> #left_join(testAvgE1,by=c("id","condit","bandInt")) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))

@@

constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
comparison_EXAM <- constant_EXAM - varied_EXAM
summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")
#print(summary_EXAM)

@@

```{r}
#| label: fig-cm-vx-pat
#| fig-height: 12
#| fig-width: 11

@@

@@

```{r}
#| label: tbl-htw-modelError-e23

@@

bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
  select(1,2,4,5,6) %>%
  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
  tibble::remove_rownames() %>%
  mutate(Term = stringr::str_remove(Term, "b_")) %>%
  kable(booktabs = TRUE)

@@

e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3")) 
# |> 
#   flextable::tabulator(rows=c("Task Stage","Fit_Method","Model"), columns=c("Exp", "condit"),
#                        `ME` = as_paragraph(mean_error)) |> flextable::as_flextable()

wide_data <- e23_tab %>%
  pivot_wider(
    names_from = c(Exp, Model, condit),
    values_from = mean_error,
    names_glue = "{Exp}_{Model}_{condit}"
  ) %>%
  arrange(Fit_Method, `Task Stage`)  # Sort for clarity

# Create a gt table with the wider data
gt_table <- wide_data %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Fit Method, Task Stage, and Experiment",
    subtitle = "Comparison across Conditions and Models"
  ) %>%
  cols_move_to_start(columns = c(`Task Stage`)) %>% # Move Task Stage column to the start
  cols_label(
    `Task Stage` = "Task Stage"
  ) %>%
  fmt_number(
    columns = matches("E2|E3"),
    decimals = 1  # Adjust the number of decimal places as needed
  ) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_style(
    style = cell_fill(color = "white"), # Ensure readability in grayscale
    locations = cells_body(columns = everything(), rows = everything())
  ) %>%
  tab_style(
    style = cell_borders(sides = "top", color = "black", weight = px(1)),
    locations = cells_body(columns = everything(), rows = everything())
  ) %>%
  tab_options(
    column_labels.font.size = 10,
    heading.title.font.size = 14,
    heading.subtitle.font.size = 12,
    table.font.size = 10,
    quarto.disable_processing = TRUE
  ) %>%
  tab_footnote(
    footnote = "Note: Mean errors are calculated as the absolute difference between the predicted and actual values.",
    locations = cells_title(groups = "subtitle")
  )

gt_table

@@

bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
  select(1,2,4,5,6) %>%
  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
  tibble::remove_rownames() %>%
  mutate(Term = stringr::str_remove(Term, "b_")) %>%
  kable(booktabs = TRUE)

```{r}
#| label: fig-e2_e3_ae
#| fig-cap: "Conditional effects of Model and Condition on Model Error for Experiment 2 and 3 data."
#| fig-height: 11
#| fig-width: 11

p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
  ggplot2::xlab("Condition") +ylab("Model Error") + labs(title="E2. Model Error")
p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
  labs(x="Model",y=NULL)
p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
  scale_color_manual(values=wes_palette("Darjeeling1")) +
  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")

@@

bm1 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
bm2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
bm3 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")

@@

 #p2 <- (p1 + p2+ p3)

#modelsummary::modelsummary(list("e1"=e1_ee_brm_ae,"e2"=e2_ee_brm_ae,"e3"=e3_ee_brm_ae), gof_map = tribble())

 (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")

@@

```{r}
#| fig-height: 10
#| fig-width: 11
#| fig-cap: "Empirical data and Model predictions from Experiment 2 and 3 for the testing stage. Observed data is shown on the right. "

>>>>

invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
invisible(list2env(load_e1(), envir = .GlobalEnv))

e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
```

@@

#  post_dat |> group_by(id,condit,Model,Fit_Method) |> summarise(y=mean(y), pred=mean(pred), ae=abs(y-pred)) |>
#     group_by(id,condit,Model,Fit_Method) |> 
#     summarise(mean_error=mean(ae)) |> 
# ggplot(aes(x=mean_error,fill=condit,y=interaction(Model,Fit_Method))) + stat_halfeye()
# 
#  post_dat |> group_by(id,condit,Model,Fit_Method,x) |> summarise(y=mean(y), pred=mean(pred), ae=abs(y-pred)) |>
#     group_by(id,condit,Model,Fit_Method,x) |> 
#     summarise(mean_error=mean(ae)) |> 
#   ggplot(aes(x=mean_error,fill=condit,y=interaction(Model,Fit_Method))) + 
#   stat_halfeye() +
#   facet_wrap(~x)

@@

```{r}
#| label: fig-htw-post-dist
#| fig-cap: "Posterior Distributions of $c$ and $lr$ parameters. Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median. Note that the y axes of the plots for the c parameter are scaled logarithmically."
#| fig-height: 6
#| fig-width: 10

@@

lr_post <- post_dat_avg %>%
    group_by(id, condit, Model, Fit_Method, rank) %>%
    slice_head(n = 1) |>
    ggplot(aes(y=lr, x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.4)) +
    ggh4x::facet_nested_wrap(~Model) + labs(title="learning rate parameter") +
  theme(legend.title = element_blank(), legend.position = "none",plot.title=element_text(hjust=.5))
c_post + lr_post

# post_dat_avg %>%
#     group_by(id, condit, Model, Fit_Method, rank<3) %>%
#     slice_head(n = 1) |>
#     ggplot(aes(y=interaction(Model,Fit_Method), x = c, col=condit)) + 
#   #stat_pointinterval(position=position_dodge(.2)) +
#  # geom_freqpoly() +
#   scale_x_continuous(trans='log10')+
#   stat_halfeye() +
#   #geom_density() +
#    # ggh4x::facet_nested_wrap(~Model) + 
#   labs(title="c parameter") +
#   theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4))
# 
#     
#     p1 <- post_dat_avg |> group_by(id,Model,Fit_Method,condit) |> 
#     summarise(c=median(c),lr=median(lr)) |> 
#       group_by(Model,Fit_Method,condit) |> 
#       mutate(c=scale(c),lr=scale(lr)) |> 
#       #ggplot(aes(scale(c),scale(lr),color=condit))+
#       ggplot(aes(c,lr,color=condit))+
#       geom_point() +
#       scale_x_continuous(trans='log10')
#     
#     ggExtra::ggMarginal(p1, groupColor=TRUE,groupFill = TRUE)

@@

```{r}
#| fig-caption: Marginal differences
#| fig-height: 9
#| fig-width: 6

@@

pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
  filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))

@@

library(tidybayes)
library(emmeans)

constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
comparison_EXAM <- constant_EXAM - varied_EXAM
summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")

# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NULL)
# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NA)

  # full set of Model x condit contrasts

# ALM - EXAM
btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
  pluck("contrasts") |> 
  gather_emmeans_draws() |> 
  group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())

# btw_model |> ggplot(aes(x=value,y=contrast,fill=condit)) +stat_halfeye()

# Constant - Varied
emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
  group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
# btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()

e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
  pluck("contrasts") |>
  gather_emmeans_draws() |> 
  group_by(contrast,.draw) |> summarise(value=mean(.value), n=n()) |> 
  filter(!(contrast %in% c("ALM Constant - EXAM Constant","ALM Constant - EXAM Varied","ALM Varied - EXAM Varied ", "EXAM Constant - ALM Varied" ))) |> 
  ggplot(aes(x=value,y=contrast,fill=contrast)) +stat_halfeye()

# {btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()} +
# {btw_model |> ggplot(aes(x=value,y=contrast,fill=condit)) +stat_halfeye()}

# emm_models_bandint_specific <- e1_ee_brm_ae |>
#   emmeans(~ Model | condit, at = list(bandInt = c(100,350,600,800,1000,1200)),
#           re_formula = NA)
# 
# 
# emm_models_bandint_by_levels <- e1_ee_brm_ae |>
#   emmeans(~ Model | condit | bandInt, 
#           at = list(bandInt = c(100,350,600,800,1000,1200)),
#           re_formula = NULL, by = "bandInt")

# within_condition_bandint_by_levels_contrasts <- emm_models_bandint_by_levels |>
#   pairs()
# 
# emm_models_bandint_by_levels |> as_tibble()

# emm_models_bandint_by_levels |> pairs() |> gather_emmeans_draws() |> 
#   as_tibble() |> group_by(bandInt,condit) |> tidybayes::median_hdi(.value) |>
#   ggplot(aes(x=.value,y=condit,fill=condit)) + stat_halfeye() +facet_wrap(~bandInt,ncol=1)

#print(summary_EXAM)

@@

```{r}
#| label: fig-cm-vx-pat
#| fig-height: 11
#| fig-width: 10

@@

(pemp1)  / pmod1 + 
  plot_layout(design = layout, heights = unit(c(5,7),c('cm','cm'))) #heights = unit(c(5,-5, 8), c('cm','null'))

@@

```{r}
#| label: tbl-htw-modelError-e123
#| tbl-cap: "Results of Bayesian Regression models predictin model error as a function of Model (ALM vs. EXAM), Condition (Constant vs. Varied), and the interaction between Model and Condition. The values represent the estimate coefficient for each term, with 95% credible intervals in brackets.  The intercept reflects the baseline of ALM and Constant. The other estimates indicate deviations from the baseline for the EXAM mode and varied condition. Lower values indicate better model fit."

@@

bm1 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
bm2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
bm3 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")
# bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
#   select(1,2,4,5,6) %>%
#   setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
#   mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
#   tibble::remove_rownames() %>%
#   mutate(Term = stringr::str_remove(Term, "b_")) %>%
#   kable(booktabs = TRUE)

@@

@@

# bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
#   select(1,2,4,5,6) %>%
#   setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
#   mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
#   tibble::remove_rownames() %>%
#   mutate(Term = stringr::str_remove(Term, "b_")) %>%
#   kable(booktabs = TRUE)

msa <- modelsummary::modelsummary(list("Exp 1."=e1_ee_brm_ae,"Exp 2."=e2_ee_brm_ae,"Exp 3. "=e3_ee_brm_ae), 
    gof_map = NA,
    fmt=1,
    estimate = "{estimate}",
    statistic="[{conf.low}, {conf.high}]", 
    coef_omit = "^sigma|^sd|^cor",
    coef_rename=function(x) stringr::str_remove(x, "b_"), output="gt")

msa

#library(modelsummary)
# modelsummary::modelsummary(get_estimates(e1_ee_brm_ae, test = c("pd")),gof_map = NA)
#modelsummary::get_estimates(e1_ee_brm_ae,test="pd")
```

e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3"))

gt_table <- e23_tab %>%
  pivot_wider(
    names_from = c(Exp, Model, condit),
    values_from = mean_error,
    names_glue = "{Exp}_{Model}_{condit}"
  ) %>%
  arrange(Fit_Method, `Task Stage`) %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Fit Method, Task Stage, and Experiment",
    subtitle = "Comparison across Conditions and Models"
  ) %>%
  cols_move_to_start(columns = `Task Stage`) %>%
  cols_label(`Task Stage` = "Task Stage") %>%
  fmt_number(columns = matches("E2|E3"), decimals = 1) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_style(
    style = list(
      cell_fill(color = "white"),
      cell_borders(sides = "top", color = "black", weight = px(1))
    ),
    locations = cells_body(columns = everything(), rows = everything())
  ) %>%
  tab_options(
    column_labels.font.size = 10,
    heading.title.font.size = 14,
    heading.subtitle.font.size = 12,
    table.font.size = 10,
    quarto.disable_processing = TRUE
  ) %>%
  tab_footnote(
    footnote = "Note: Mean errors are calculated as the absolute difference between the predicted and actual values.",
    locations = cells_title(groups = "subtitle")
  )

gt_table
```

```{r}
#| label: fig-e2_e3_ae
#| fig-cap: "Conditional effects of Model and Condition on Model Error for Experiment 2 and 3 data."
#| 
#| fig-height: 5
#| fig-width: 9

#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
  ggplot2::xlab("Condition") +ylab("Model Error") + labs(title="E2. Model Error")
p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
  labs(x="Model",y=NULL)
p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
  scale_color_manual(values=wes_palette("Darjeeling1")) +
  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")

@@

@@

 #p2 <- (p1 + p2+ p3)
 (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")

@@

```{r}
#| fig-height: 8
#| fig-width: 10
#| fig-cap: "Empirical data and Model predictions from Experiment 2 and 3 for the testing stage. Observed data is shown on the right. "

### 2024-03-24 Model/htw_model_e1.qmd
let's try that again

pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) 
pd <- post_dat |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt"))

pdl |> group_by(id,condit, bandType,Resp) |>
 summarize(dist=mean(dist)) |> ggplot(aes(x=Resp,y=dist, fill=condit)) + stat_bar + facet_wrap(~bandType)

@@

b3 <- brm(data=pd |> filter(rank==1),
  mean_error ~ Model*id, 
  file = paste0(here("data/model_cache/e1_brms_examEst_ModelxID.rds")),
  chains=2, iter=500, control=list(adapt_delta=0.92, max_treedepth=11))
summary(b3)

@@

k |> ggplot(aes(x=parType,y=Estimate,fill=condit)) + geom_boxplot()

# plot Model coefficients for each individual

@@

>>>>

# pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) 
# pd <- post_dat |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt"))

# pdl |> group_by(id,condit, bandType,Resp) |>
#  summarize(dist=mean(dist)) |> ggplot(aes(x=Resp,y=dist, fill=condit)) + stat_bar + facet_wrap(~bandType)

library(emmeans)
library(brms)
library(tidybayes)
options(brms.backend="cmdstanr",mc.cores=1)

invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
invisible(list2env(load_e1(), envir = .GlobalEnv))

e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())

pdl <- post_dat_l |> rename("bandInt"=x) |> #left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
    filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))

pdl_all <- post_dat_l |> rename("bandInt"=x) |> #left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
    filter(rank<=1, !(Resp=="Observed")) |> mutate(aerror = abs(error))

pd <- post_dat_avg |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
    filter(rank<=1,Fit_Method=="Test_Train")  |> mutate(aerror = abs(error))

d1 <- pdl |> group_by(id,condit,bandInt) |> slice_head(n=1)

d1 |> group_by(condit) |> summarize(c=median(c),lr=median(lr))

pdl |> group_by(condit,Model) |> summarize(me=mean(error),ae=mean(aerror))
pdls_sum <- pdl |> group_by(id, condit,Model,bandInt) |> summarize(me=mean(error),ae=mean(aerror)) |> 
  group_by(id,condit, Model) |> summarize(me=mean(me),ae=mean(ae))
pdls_sum_b <- pdl |> group_by(id, condit,Model,bandInt) |> summarize(me=mean(error),ae=mean(aerror))
# id    condit   Model    me    ae
#    <fct> <fct>    <chr> <dbl> <dbl>
#  1 1     Varied   ALM    72.7 108. 
#  2 1     Varied   EXAM   34.5  63.3
#  3 2     Varied   ALM   135.  138. 
#  4 2     Varied   EXAM   75.5  84.0

# for each id and condit - add a column indicating which model had the lower error
pdls_sum |> group_by(id,condit) |> 
  mutate(ModelEXAM = ifelse(me[Model=="EXAM"] < me[Model=="ALM"],"EXAM","ALM")) |> 
  group_by(condit,ModelEXAM) |> 
  summarize(n=n(),me=mean(me),ae=mean(ae)) |> 
  ggplot(aes(x=ModelEXAM,y=me,fill=condit)) + geom_col() + facet_wrap(~condit)

pdls_sum_b |> group_by(id,condit,bandInt) |> 
  mutate(ModelEXAM = ifelse(me[Model=="EXAM"] < me[Model=="ALM"],"EXAM","ALM")) |> 
  group_by(condit,ModelEXAM,bandInt) |> 
  summarize(n=n(),me=mean(me),ae=mean(ae)) |> 
  ggplot(aes(x=ModelEXAM,y=me,fill=condit)) + geom_col() + facet_wrap(~bandInt)

formula <- bf(aerror ~ condit + (1 + condit | id) + (1 + condit | Model))
model <- brm(formula, data=pdl, chains=1,iter=500)

formula <- bf(error ~ condit * Model + c + lr + (1 + condit * Model + c + lr | id))
modelp <- brm(formula, data=pdl, chains=1,iter=900)
summary(modelp)
wrap_plots(plot(conditional_effects(modelp),points=FALSE,plot=FALSE))
plot(emmeans(modelp, ~ c | Model), type = "response")
plot(emmeans(modelp, ~ lr | Model), type = "response")

formula <- bf(error ~ condit * Model + c + lr + (1 + condit * Model + c + lr | id))
modelp <- brm(formula, data=pdl, chains=1,iter=900)

formula <- bf(dist ~ condit*vb + c + lr + (1 + condit*vb| id)) 
d1 <- pdl |> group_by(id,condit,bandInt, Model) |> slice_head(n=1)

m_dist <- brm(formula=formula,chains=1,
      data = d1 ,
      iter=900)

summary(m_dist)
wrap_plots(plot(conditional_effects(m_dist),points=FALSE,plot=FALSE))
emmeans(m_dist, ~ condit+lr)
emmeans(m_dist, ~ condit+c)
individual_preds <- fitted(m_dist, re_formula = NULL) %>% data.frame() %>% bind_cols(d1)

formula_dist <- bf(dist ~ condit * Model* c + lr + (1 + c * lr || id))
model_dist <- brm(formula_dist,data=d1, iter=2100, chains=2) 
summary(model_dist)
 bayestestR::describe_posterior(model_dist)
wrap_plots(plot(conditional_effects(model_dist),points=FALSE,plot=FALSE))

testAvgE1 |> group_by(vb) |> 
ggplot(aes(x=vb,y=distAvg)) + 
  #stat_pointinterval(position=position_dodge(.5), alpha=.9) 
  geom_col()

model_dist_std <- d1 %>%
  mutate(c_std = scale(c),
         lr_std = scale(lr)) %>%
  brm(
    bf(dist ~ bandType * condit * c_std * lr_std + (1 + bandType * condit * c_std * lr_std | id)),
    family = gaussian(),
    prior = c(
      prior(normal(0, 10), class = Intercept),
      prior(normal(0, 10), class = b),
      prior(cauchy(0, 5), class = sd),
      prior(lkj(2), class = cor)
    ),
    iter = 4000,
    warmup = 2000,
    chains = 4,
    cores = 4
  )

# fit brms model to determine which model is the better fit for each id and condit
b4 <- brm(data=pdl |> filter(rank==1),aerror ~ Model + (1+Model|id), chains=1, iter=500, control=list(adapt_delta=0.92, max_treedepth=11))

# visualize the strength of the evidence for each model, for each id
coef(b4)$id[,, 'ModelEXAM']  %>% tibble::as_tibble(rownames="id") |> ggplot(aes(x=Estimate)) + geom_histogram()

@@

b_id <- brm(data=pdl |> filter(rank==1),
  aerror ~ Model + (1+Model|id), 
  file = paste0(here("data/model_cache/e1_brms_e_rf_id1.rds")),
  chains=1, iter=500, control=list(adapt_delta=0.92, max_treedepth=11))
summary(b5); bayestestR::describe_posterior(b5)
wrap_plots(plot(conditional_effects(b_id),points=FALSE,plot=FALSE))
coef(b_id)$id[,, 'ModelEXAM']  %>% tibble::as_tibble(rownames="id") |> ggplot(aes(x=Estimate)) + geom_histogram()

b_vb <- brm(data=pdl, aerror ~ Model*condit*vb + (1+vb*Model|id), chains=1, iter=900)
wrap_plots(plot(conditional_effects(b_vb),points=FALSE,plot=FALSE))
individual_preds <- fitted(b_vb, re_formula = NULL) %>% data.frame() %>% bind_cols(pdl)
emmeans(b_vb, ~ condit * Model)
plot(emmeans(b_vb, ~ condit * Model))
b_vb %>% emmeans(specs = ~ Model * condit) %>% pairs()

b5 <- brm(data=pdl |> filter(rank==1),
  error ~ Model + (1+Model|condit:id), 
  file = paste0(here("data/model_cache/e1_brms_e_rfX_id1.rds")),
  chains=1, iter=500, control=list(adapt_delta=0.92, max_treedepth=11))
summary(b5); bayestestR::describe_posterior(b5)

id_ee1 <- coef(b5)$id[,, 'ModelEXAM']  %>% tibble::as_tibble(rownames="id") |> 
  left_join(ranef(b4)$id[,, 'ModelEXAM']  %>% tibble::as_tibble(rownames="id") |> transmute(id=id,ranef=Estimate),by="id")

left_join(e1Sbjs,by="id")
ranef(b4)$id[,, 'ModelEXAM']  %>% tibble::as_tibble(rownames="term")

hypothesis(b4, "ModelALM:conditVaried < ModelEXAM:conditVaried")

id_ee1 <- coef(b5)$`condit:id`[,, 'ModelEXAM']  %>% tibble::as_tibble(rownames="id")
# id           Estimate Est.Error  Q2.5 Q97.5
#    <chr>           <dbl>     <dbl> <dbl> <dbl>
#  1 Constant_10     -21.0      18.2 -64.4  9.43
#  2 Constant_101    -11.6      14.6 -34.0 21.2 
#  3 Constant_102    -16.5      16.5 -51.7 16.3

# split id into condit (Constant or Varied) and id (number between 1-250 - occurs after the _)
id_ee1 |> mutate(condit=word(id,1,sep="_"),id=word(id,2,sep="_")) |> 
    left_join(e1Sbjs,by=c("id","condit")) |> 
    ggplot(aes(x=id,y=Estimate,fill=condit)) + 
    geom_col() + facet_wrap(~condit, scales="free_y")

individual_preds <- fitted(b4, re_formula = NA) %>% data.frame() %>% bind_cols(pdl)

#coef(b4)$id[,, 'ModelEXAM']  %>% tibble::as_tibble(rownames="term")
# A tibble: 156 × 5
   term  Estimate Est.Error   Q2.5   Q97.5
   <chr>    <dbl>     <dbl>  <dbl>   <dbl>
 1 1        -37.7      20.9  -74.1   8.80 
 2 2        -46.2      21.0  -87.8   1.09 
 3 3        -95.5      21.1 -145.  -61.2  
 4 4        -42.8      20.8  -80.6  -0.263
 5 5        -88.3      20.0 -128.  -54.9

# ranef(b4)$id[,, 'ModelEXAM']
#     Estimate Est.Error      Q2.5    Q97.5
# 1    21.8534      20.8  -14.9709  65.8017
# 2    13.3688      20.2  -24.7168  60.5872
# 3   -35.9294      20.4  -85.8305  -1.0799

fixef(b4)
#    fixef(b4)
#           Estimate Est.Error  Q2.5 Q97.5
# Intercept    193.1      7.18 177.6   205
# ModelEXAM    -59.5      6.83 -71.8   -45

fe <- fixef(b4)[,1]
id_ee1 |> mutate(id=reorder(id,Estimate)) |> 
 left_join(e1Sbjs,by="id") |>
  ggplot(aes(x=id,y=Estimate,fill=condit)) + 
  geom_col() +  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y") + coord_flip()

 data.frame(ranef(b4, pars = "ModelEXAM")$id[, ,'ModelEXAM']) %>% 
  tibble::rownames_to_column("id") %>% 
  left_join(e1Sbjs, by = "id") |> 
  mutate(intercept = fixef(b4)[,1]["Intercept"], 
          #cond= fe["conditVaried"]*(condit=="Varied"),
           int= fe["ModelEXAM:conditVaried"]*(condit=="Varied" & Model=="EXAM"), 
         slope = Estimate + adjust)

 data.frame(coef(b4, pars = "ModelEXAM")$id[, ,'ModelEXAM']) %>% 
  tibble::rownames_to_column("id") %>% 
  left_join(e1Sbjs, by = "id")

b3 <- brm(data=pdl |> filter(rank==1),
  aerror ~ Model*id, 
  file = paste0(here("data/model_cache/e1_brms_ee_ModelxID.rds")),
  chains=1, iter=500, control=list(adapt_delta=0.92, max_treedepth=11))
summary(b3)

wrap_plots(plot(conditional_effects(b5),points=FALSE,plot=FALSE))

plot(conditional_effects(b5, 
                         effects = "Model:condit", 
                         conditions=make_conditions(b5,"bandType" )),
     points=FALSE,plot=TRUE)

@@

k |> ggplot(aes(x=parType,y=Estimate,fill=condit)) + geom_boxplot()
# plot Model coefficients for each individual

@@

mcmc_plot(b3,variable=c("b_ModelExam"),regex=T)
